An HPSG account for verbal reduplication in Mandarin Chinese

### 2024-07-15 replies-reviews.tex

It is worth noticing that, different from diminishing verb reduplication, in AABB verbal reduplication (which has a different meaning and function), the perfective aspect marker /e can never be placed inside the reduplicated verb but can be put at the end of the AABB pattern. Also, I do not understand the comparison with SVCs. Let’s say that reduplication is a syntactic phenomenon, but that does not mean that it is a SVC, i.e. a sequence of verbs or verb phrases in a relation of coordination or subordination, which are basically independent of each other. It could simply be another type of syntactic construction with its specific properties.

3) Phrasal substitution. The inclusion of this test is questionable since reduplication primarily targets verbs and not phrases. Therefore, syntactic objects should not be included in the reduplication; it is not repetition of phrases. Indeed, if the object is part of a non-separable verb-object compound (which is a lexical unit), it is included in the reduplication (F</0> 0> guan-xin guan-xin/*  K> guan-guan xin vs. WsBkE tico-tiao wii | * B FEBEE ticown tiaowii).

4) Conjunction reduction. This criterion can only be applied to set apart coordinated phrases from coordinate compound words with a head in common (e.g. ‘K huiché e ¥4 giché in (33) share the head  ché ‘vehicle’). But the examples provided by the author(s) to argue against conjunction reduction with reduplicated verbs are completely different: the verbs do not have the head in common (exx. 34). I believe that this is not a reasonable test to argue for the wordhood of reduplicated verbs.

In summary, the tests used to support the morphological status of reduplication appear
unconvincing.

%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%
\textbf{Answer:}
Based on the suggestions by the reviewers and further literature research, this section is drastically revised.
The tests of semantic compositionality and conjunction reduction are deemed unreliable.
\citet[37--38]{Dai1992}, \citeyear[120--122]{Dai1998} explains the problems of conjunction reduction (he calls it ``coordination'').
That leaves us with phrasal extension (or ``modification'' according to \citealt[32]{Dai1992}, \citeyear[117]{Dai1998})
and phrasal substitution (or ``expansion'' according to \citealt[33]{Dai1992}, \citeyear[117--120]{Dai1998}).
These tests requires further clarifications.

@@

The comparison with Parallel Verb Compounds and Serial Verb Constructions only serves to facilitate understanding
by contrasting the behaviors of different multi-verb constructions in Mandarin Chinese,
but this does not contribute to the arguments in any substantial way.
Due to the critics from the reviewers, this comparison is removed.

Cross-linguistically, verbal reduplication in Mandarin Chinese patterns more with morphological reduplication (below as reduplication) in other languages
than syntactic reduplication (below as repetition \citealt[31]{Gil2005}, \citealt[1--2]{Forza2016}).
\citet[35--36]{Gil2005} considers non-iconicity and having only two copies as sufficient but not necessary conditions for reduplication.
He further proposes building one intonational group as sufficient and necessary condition for reduplication (p. 36).
All three conditions are true for verbal reduplication in Mandarin Chinese.
% one intonational group \citep[154]{Sui2018}
\citet[9]{Forza2016} argues that the substantial difference between reduplication and repetition lies in the fact that only the former affects grammatical features such as aspect.
This is also true for verbal reduplication in Mandarin Chinese.

In sum, we maintain that verbal reduplication in Mandarin Chinese is better off analyzed as a morphological phenomenon.

%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%
%%%%YL
\item
Sect. 3.3: I cannot understand the parallel with Mandarin verbal reduplication. The
author(s) say(s): “The following section discusses previous literature which proposed a special
construction for the reduplication”. However, it becomes evident that the phenomenon under
examination is entirely different from Mandarin verbal reduplication. Ghomeshi et al. (2004) analyze
a phenomenon which is well attested in world languages, even in those without productive
reduplication, i.e. contrastive focus reduplication/repetition, which involves the repetitions of
words and sometimes phrases (Oh, we re not LIVING-TOGETHER-living-together, Gomeshi et al. 2004: 308). Their function is “to focus the denotation of the reduplicated element on a more sharply delimited, more specialized, range” (Gomeshi etal. 2004: 308); for example, in ex. (47) cited by the author(s) SALAD-salad means green salad vs. salads in general. This has nothing to do with diminishing verbal reduplication in Mandarin. The authors’ endeavor to apply the analysis proposed for contrastive focus reduplication to Mandarin verbal reduplication raises questions about its rationale (why? These two phenomena are fundamentally distinct and serve different linguistic functions). Consequently, attempting to employ the same analytical framework for both is problematic, and, indeed, the author(s) conclude(s) that: “this approach fails to account for the similarities of the reduplication and other aspect markers in Mandarin Chinese”. This is precisely because contrastive focus repetition/reduplication is a different phenomenon with a different function, and Mandarin verbal reduplication cannot be analyzed in the same way. Furthermore, the author(s) suggest(s) that this approach “[...] also provides a formal account for the phonology of the reduplication”. However, contrastive focus reduplication/repetition generally does not involve morpho-phonological readjustment phenomena, which are typically found in reduplication. As a result, it cannot adequately account for phenomena such as the neutral tone of the reduplicant in the case of reduplication of monosyllabic verbs (kan > kan kan).

%%%%%%%%%%%%%%%%%%
\textbf{Answer:}
Since the reviewer deemed it irrelevant, the section concerning \citet{Ghomeshietal2004} is removed.

%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%
%% YL
\item Pp. 26, lines 24-25: ``The output reduplicates the phonology (phon) of the input verb with the possibility to have further phonological material in between. [] indicates an underspecified list which could be empty or not''. However, it is not entirely clear what prevents phonological material other than yi and le to appear in between the reduplicated elements. This aspect seems to be somewhat arbitrary, and it is not evident why certain elements are permissible while others are not.

%%%%%%%%%%%%%%%%%%%%
\textbf{Answer:}
\obj{le} `\textsc{pfv}' marks the perfective aspect.
The reason for \obj{le} `\textsc{pfv}' being the only aspect marker compatible with reduplication is explained in the Semantics Section.

@@

Synchronically, A-\obj{yi}-A has the same meaning as AA and both do not refer to the actual number of the event denoted by the verb.
This means that \obj{yi1} `one' in A-\obj{yi}-A does not contribute any specific meaning to the structure
and is only there as a historical remnant.
In this sense,  \obj{yi1} `one' appearing in between the reduplication is synchronically arbitrary. %similar to linking elements in compounds

Besides the obvious conceptual reason that  \obj{yi1} `one' means `little, few',
there might be a phonological explanation for  \obj{yi1} `one' rather than other numerals is used in the A-\obj{yi}-A structure.
In Chinese, one form of intensifying reduplication is A-\obj{li}-AB e.g. \obj{hu2-li-hu2tu2} `confused-li-confused',
where the \obj{li} is fixed and also does not bear any meaning.
\citet[137]{Sui2018} assumes that this syllable is filled with \obj{li} because the open syllable \obj{li} is a relatively unmarked phonological constituent \citep{Yip1992}
and the second syllable in A-\obj{li}-AB occupies an unstressed position.
We can see the similarities between \obj{li} in A-\obj{li}-AB and \obj{yi} in A-\obj{yi}-A: they are both relatively unmarked and occupies an unstressed position.
This can also make it easier for  \obj{yi1} `one' rather than other numerals to become part of a fixed structure.
But a phonological account is out of the scope of this paper and has to be left for further research.

The subtypes of \type{verbal-reduplication-lr} prevent phonological materials other than \phonliste{le} and \phonliste{yi} from appearing in between the reduplication by specifying what can appear in the list and what not.

%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%
%% YL
\item
The proposed analysis appears to have limitations in explaining the constraints on verbs and the observed modifications at the Aktionsart level. How can one determine which verbs are exempt from the proposed lexical rule? The proposed rule does not seem to provide a clear prediction of which verbs are allowed and which are excluded from reduplication. Why only some states and achievements are allowed? The restrictions on the usage of the progressive with reduplicated verbs also remain unexplained.

%%%%%%%%%%%%%%%%%%%%%
\textbf{Answer:}
As explained above, we propose that all verbs regardless of their basic Aktionsart can be reduplicated given suitable context.
The incompatibility with the progressive aspect marker is explained in the Semantics section.
%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%
%% Stefan
\item
The proposed analysis appears to have a descriptive rather than an explanatory power.
%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%

\textbf{Answer:} \itdopt{Stefan, say something.}

%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%
%% YL
\item
I would add tones to the pinyin transcription.

%%%%
\textbf{Answer:} done

%%%%%
%Other comments:
\item
p. 4: ex. (8b) is interesting, since it appears to involve the reduplication of V1 of a resultative compound. To the best of my knowledge, exiting literature on the subject consistently maintains that resultative compounds are not amenable to reduplication.

%%%%%%%%

\textbf{Answer:} add footnote

%%%%%%%%
\item
p. 5, exx. (11): I believe it would be useful to provide also an example illustrating that reduplicated verbs are incompatible with (post-verbal) for X-time adverbials.
%%%%

\textbf{Answer:} See above.

%%%%
\item
p. 18, exx. (39b): to the best of my knowledge, the object can be placed before —F yixia only in limited cases (pronouns and proper nouns).
%%%%%%%%%%%%%

\noindent
\textbf{Answer:}
There are some examples from the corpus showing that not only pronouns and proper nouns can be placed before \obj{yi2} \obj{xia4} `once':
\ea%她看了他的脸一下。(CCL)
\gll \objex{ta1} \objex{kan4-le} \objex{ta1de} \objex{lian3} \objex{yi2} \objex{xia4}.\\
she look-\textsc{pfv} his face one time\\\jambox{(CCL)}
\glt `She took a look at his face.'

@@

\ex%他没碰窗户，就看了玻璃一下，玻璃就烂了。(CCL)
\gll \objex{ta1} \ldots\, \objex{jiu4} \objex{kan4-le} \objex{bo1li} \objex{yi2} \objex{xia4}, \objex{bo1li} \objex{jiu4} \objex{lan4-le}.\\
he {} just look-\textsc{pfv} glass one time glass just break-\textsc{pfv}\\\jambox{(CCL)}
\glt `He just took a look at the glass and the glass just broke.'
\z
We think it has to do with the weight/length of the object, i.e. shorter objects can be placed before  \obj{yi2} \obj{xia4} `once' while longer ones cannot.
%This is not necessarily a syntactic constraint

Even if we accept that the object can be only be placed before  \obj{yi2} \obj{xia4} `once' in limited cases,
the fact that the object can be placed before  \obj{yi2} \obj{xia4} `once' in some cases but in no cases in between reduplication suggests there is a fundamental difference between the structure of the two phenomena.

%%%%%%%%%%%%%%
\item
p. 20, lines 28-31: “Arcodia et al. (2014) and Basciano \& Melloni (2017) assumed that the first
element in the reduplication is the actual verb, which resides under init and proc, and that the
second element is an aspect marker, which resides in the complement position of proc, as it delimits
the process of the event”. Based on my understanding, these authors do not claim that the second
element serves as an aspect marker. They propose that the verb and the reduplicant are the spell-out
of two copies of the same lexical item within the vP domain: the reduplicant is the lower copy, in
complement position, and serves as an event delimiter. In this analysis, reduplication affects the Aktionsart of the verb.

%%%%%%%%%%%%%
\noindent
\textbf{Answer:} We reformulated as ``The second element is the copy of the verb, which resides in the complement position of proc and serves as an event delimiter.''

%%%%%%%%%%%%%
\item
p. 32, lines 28-34: “Although these forms are generally considered unacceptable (Li \& Thompson 1981: 30; Hong 1999: 275-276; Basciano \& Melloni 2017: 160; Yang \& Wei 2017: 239), Fan (1964: 269) and Sui (2018: 143) considered AB-yi-AB and AB-le -yi-AB to be possible, even though they both recognized that these two forms are rare.” Given that these patterns were possible in previous stages of the language (see a.0. Basciano \& Melloni 2017), these rare occurrences can be seen as relics of this usage.

%%%%%%%%%%%%%%%%%%%%%%
\textbf{Answer:} add a footnote
%%%%%%%%%%%%%%%%%%%%%%
\end{enumerate}

\section{Reviewer 2}
\begin{enumerate}
\item
This paper presents an innovative analysis of verb reduplication in Mandarin Chinese, demonstrating
clarity and well-organized sections. To enhance clarity, I recommend providing a brief illustration for
technical terms like LTOP, catering to readers less familiar with them.
The authors employ various tests to assert that verb reduplication exhibits more word-like
characteristics than phrase-like, hence justifying its morphological classification. The subsequent
adoption of a Head-Driven Phrase Structure Grammar (HPSG) framework, integrating Minimal
Recursion Semantics (Copestake et al., 2005), presents advantages over prior analyses.
Despite these strengths, certain questions warrant attention. The primary concern revolves around
treating verb reduplication as morphological. The authors compare it with Parallel Verb Compound
(PVC) and Serial Verb Construction (SVC), asserting that verb reduplication aligns more closely with
SVC than PVC in tests like phrase extension, substitution, and conjunction reduction. However, the
choice of SVC over regular verb phrases as a point of comparison with PVC and verb reduplication
lacks clarity. While SVC passes these tests, it is crucial to note that regular verb phrases may not pass
some, e.g., separate modification of subparts within a constituent.
In light of this, concluding that verb reduplication is more word-like and less phrase-like is
questionable, as regular verb phrases encounter similar challenges. Therefore, it is crucial to
explicitly justify why SVC was chosen over regular verb phrases for this comparison. Providing such
clarification will strengthen the robustness of the paper's argumentation and render the conclusion
that verb reduplication should be morphological more convincing.
For additional comments, please refer to the attached PDF file.

@@

%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%
%% YL
R2 comments on the following passage: The current study will only focus on the AA, A-yi-A, A-le-A, A-le-yi-A, ABAB and
AB-le-AB forms of verbal reduplication in Mandarin Chinese. AA-kan, A-kan-kan,
AAB, A-yi-AB, A-le-AB will also be mentioned.

One of the key questions addressed in this paper pertains to whether verb reduplication is best understood as a morphological or a syntactic phenomenon. However, it's noteworthy that the forms emphasized in this paper are all instances of syntactic verb reduplication (Xie, 2020).

To further enrich the ongoing debate, I wonder whether the authors will consider the inclusion of examples that previous studies have identified as morphological verb reduplications. This addition would help demonstrate the broader scope and applicability of your analysis. Alternatively, it would be beneficial to clarify the reasons for selecting these specific forms in this article.

%%%%%%%%%%%%%%%%
\noindent
\textbf{Answer:}
\citet{Xie2020} identifies the AABB form as morphological verb reduplication.
Even though we do not agree with \citegen{Xie2020} claim that the distinction between ABAB and AABB lies in the distinction between morphology and syntax,
we do agree that they are different grammatical processes and thus requires separate analyses (See also \citealt[Sec. 4.3]{Deng2013}, \citealt{Wang2023}).
Also note that there are numerous scholars that do consider the forms analyzed here as morphological processes (\citealt[Ch. 4]{Chao1968}, \citealt[Ch. 3]{LiThompson1981}, \citealt[4--5]{Liao2014} and \citealt[Sec. 4]{Sui2018}).
\citet[14--15]{Zhang2000} argues that the AABB form of reduplication develops from a completely separate historical origin from the AA and ABAB forms,
as the former has a intensifying rather than delimitative meaning.
\citet[83--84]{Xie2020} further points out that AABB is much less productive than ABAB.
This suggests that at least some AABB might not be formulated by rules but is stored in the lexicon as a whole.
This is probably the case for those AABBs that have an idiomatic meaning, such as \obj{zhi2-zhi3-dian2-dian3} `point-point-gesture-gesture, gossip'.
%Productively formed AABBs can be accounted for by the current analysis as the reduplication happens before the compounding process,
%i.e. monosyllabic verbs are reduplicated separately (as AA and BB respectively) and then compounded together to form AABB.
%This is in line with the proposal in \citet[Sec. 4.2]{Wang2023},
%and also explains why some AABBs do not have a base AB form, such as \textit{zou-zou-ting-ting} `walk-walk-stop-stop, walk for a while and rest for a while', *\textit{zou-ting} `walk-stop'
The current analysis has a broad scope in that it explains all forms of delimitative verbal reduplication, which previous analyses were not able to do.
An analysis for the AABB form of reduplication has to be left for further research.

%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%
%% YL
\item
R2 comments on the following passage: The meaning of the reduplication is not compositional, as it does
not mean that the event denoted by the verb happens twice or multiple times, but
rather that the event happens for a short duration and/or for low frequency. This
non-compositionality suggests that a reduplication is more word-like.

@@

Moreover, in Mandarin, conjunctions can only be employed with nouns and not with verbs phrases or
clauses (Schafer, 2009). If this holds true, it is less likely to observe conjunction reduction for
verb phrases. Consequently, it would be inappropriate to assert that verb reduplication is more
word-like and less phrase-like, as even regular verb phrases may encounter problems undergoing
conjunction reduction.

In Section 2.4, the authors asserted that verb reduplication is more phrase-like than word-like based on its similarities with Parallel Verb Compounds as apposed to Serial Verb Construction (SVC).

However, it is crucial to acknowledge that SVC has distinctive features, some of which diverge from those of a standard verb phrase. This raises a concern that a verb phrase might not successfully pass certain tests applicable to SVC, such as the ability for a constituent to be partially modified (A regular verb phrase like 'Verb + Object' cannot be partially modified by an adverb, while each verb in an SVC structure can be modified separately (28)). Therefore, when verb reduplication cannot be partially modified, asserting that it is less phrase-like solely on the basis of its differences from SVC might be inappropriate. This is because even a regular verb phrase faces limitations.

### 2024-07-15 replies-reviews.tex

In light of this, it becomes essential to clarify why SVC, rather than regular verb phrases, was
chosen as a comparison to Parallel Verb Compounds. Such clarification would enhance the
persuasiveness of the tests presented in this section.

%%%%%%%%%%%%%%%%%%%
\textbf{Answer:} See above.
%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%
%% YL
\item
The reason for the loss of idiomatic meaning in (43b) but not in (43c) could be attributed to the
presence of the number 'san' in (43b). If 'san xia' is replaced with 'yi xia,' which remains a
verbal classifier, the idiomatic meaning is perserved. In this case, there appears to be no
distinction between verbal classifier and reduplication.

%%%%%%%%%%%%%%%%%%%%
\noindent
\textbf{Answer}:
It is not \obj{san1} \obj{xia4} `three times' that is special, but it is \obj{yi2} \obj{xia4} `once' that is special.
We can replace \obj{san1} `three' with any number above two,
and the distinction still exist.
But \obj{yi2} \obj{xia4} `once' has acquired a duration reading `for a little while' that is not available to the other event quantifiers formed by \obj{xia4}, which only have the `for X times' interpretation (\citealt[77]{Deng2013}, \citealt[16]{Zhang2000}).
We think \obj{liang3} \obj{xia4} `twice' is following this tendency, too.
In this case, it is easy to interpret \obj{yi1} \obj{xia4} and \obj{liang3} \obj{xia4} not as referring to the actual number of action taking place,
but as duration adverbials as a whole,
thus differing them from ``actual'' verbal classifier phrases with other numerals.
%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%
%% Stefan
\item
It would enhance reader comprehension if the authors could provide a brief illustration of symbols
like HOOK, LTOP, IND, ARG, etc. This will aid readers in better grasping the authors' subsequent
proposals in Section 4.

Perhaps PHON is missed in LEX-DTR of (57), even though PHON is empty in (57).

\noindent
\textbf{Answer:} PHON is not missing. The constraints regarding PHON on the mother and the daughter are coming from
another constraint. A constraint that is a subtype in the hierarchy. The type
perfective-reduplication-lr in (51), which says that the PHON value of the daughter \ibox{1} appears
twice in the PHON value of the mother with some other material (\etag) between the two occurrences of \ibox{1}.
%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%

\end{enumerate}

@@

\section{Reviewer 3}

\begin{enumerate}
%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%
%% YL
\item
The following paragraph looks terse to me. The author(s) want to provide more explanation about the four tests. In addition, the footnote 6 might be better to move into the body.
Duanmu (1998) and Schäfer (2009) proposed the following four tests to distinguish words from phrases
in Mandarin Chinese: semantic compositionality, phrasal extension, phrasal substitution and
conjunction reduction.

In Page 14, the draft makes use of a new terminology such as “word-like”. Of course, I can understand the meaning within the context. However, I think the author(s) might be better to use a more academic and formal terminology.

%%%%%%%%%%%%%%%%%%%%%%
\textbf{Answer:} reformulate as ``behaves more similar to a word''.

%%%%%%%%%%%%%%%%%%%%%%
\item
Section 3 (Previous Analysis) appears in Page 17. I think it would be a little bit late. The author(s) may have a plan to restructure Sections 2 and 3 again.

@@

%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%
%% YL
\noindent
Answer: Since the discussion on the pros and cons of previous analyses relies heavily on understanding the syntactic and semantic constraints of reduplication, we believe that it is necessary to discuss the phenomenon thoroughly before discussing previous analyses.

%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%
%% Stefan
\item
In Page 26, the draft introduces a new notion (i.e., an empty rectangle) into the AVMs. Is it what the author(s) invent only for modeling the verbal reduplication in this drat? If so, the author(s) want to account more for how it works in AVMs. Otherwise, the author(s) might be better to refer to the previous analysis about the notion.

In Section 4, I am expecting the author(s) provide a sample derivation (maybe a tree diagram). The draft provides the subsets about how verbal reduplication can be constrained within the AVMs. On top of them, a full derivation can be made for better understanding.
%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%

\itdopt{Stefan}
\end{enumerate}

### 2024-07-20 replies-reviews.tex

%%%%%%%%%%%%%%%%%%%%%%
\textbf{Answer:} add a footnote
%%%%%%%%%%%%%%%%%%%%%%
\end{enumerate}

\section{Reviewer 2}
\begin{enumerate}
\item
This paper presents an innovative analysis of verb reduplication in Mandarin Chinese, demonstrating
clarity and well-organized sections. To enhance clarity, I recommend providing a brief illustration for
technical terms like LTOP, catering to readers less familiar with them.
The authors employ various tests to assert that verb reduplication exhibits more word-like
characteristics than phrase-like, hence justifying its morphological classification. The subsequent
adoption of a Head-Driven Phrase Structure Grammar (HPSG) framework, integrating Minimal
Recursion Semantics (Copestake et al., 2005), presents advantages over prior analyses.
Despite these strengths, certain questions warrant attention. The primary concern revolves around
treating verb reduplication as morphological. The authors compare it with Parallel Verb Compound
(PVC) and Serial Verb Construction (SVC), asserting that verb reduplication aligns more closely with
SVC than PVC in tests like phrase extension, substitution, and conjunction reduction. However, the
choice of SVC over regular verb phrases as a point of comparison with PVC and verb reduplication
lacks clarity. While SVC passes these tests, it is crucial to note that regular verb phrases may not pass
some, e.g., separate modification of subparts within a constituent.
In light of this, concluding that verb reduplication is more word-like and less phrase-like is
questionable, as regular verb phrases encounter similar challenges. Therefore, it is crucial to
explicitly justify why SVC was chosen over regular verb phrases for this comparison. Providing such
clarification will strengthen the robustness of the paper's argumentation and render the conclusion
that verb reduplication should be morphological more convincing.
For additional comments, please refer to the attached PDF file.

%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%
%% YL
\item
R2 comments on the following passage: A-\obj{kan4-kan4}

I am curious about the acceptability of this form 'A-kan-kan.' For instance, phrases like 'shuo-kan-kan' ('say-look-look') or 'ting-kan-kan' ('listen-look-look') do not seem acceptable to me.

\textbf{Answer:}
The acceptability of the A-\obj{kan4-kan4} form seems to vary among Mandarin Chinese speakers.
\citet[73]{Cheng2012} suggests that unlike AA-\obj{kan4}, A-\obj{kan4-kan4} is an emerging construction that is still undergoing grammaticalization.
He found in the Academia Sinica Balanced Corpus of Modern Chinese (Sinica Corpus, \citealt{sinica}) 23 tokens of A-\obj{kan4-kan4} but 141 tokens of AA-\obj{kan4} (p. 64).
This shows that the former is less common than the latter.
(\ref{ex:Akankan}) is an example of A-\obj{kan4-kan4} from the Sinica Corpus.
\ea\label{ex:Akankan} %就順著北風的吹勢，試看看能否將海沙攔下來吧！
\gll \objex{jiu4} \objex{shun4-zhe} \objex{bei3-feng1-de} \objex{chui1-shi4}, \obj{shi4-kan4-kan4} \objex{neng2} \objex{fou3} \objex{jiang1} \objex{hai3-sha1} \objex{lan2-xia4lai2} \objex{ba}!\\
just follow-\textsc{prog} north-wind-\textsc{de} blow-direction try-look-look can not make sea-sand block-down \textsc{ptc}\\\jambox{(Sinica Corpus)}
\glt `Let's just follow the north wind, try and see if we can block the sand!'
\z

\citegen{Cheng2012} study is based on the Mandarin spoken in Taiwan.
We might assume that A-\obj{kan4-kan4} is more widely used in Taiwan than in Mainland China.
But we also found the following examples of A-\obj{kan4-kan4} in the BCC corpus \citep{BCC}, which includes mostly data from Mainland China.
This suggests that A-\obj{kan4-kan4} is acceptable for and used by at least some Mainland Chinese Mandarin speakers as well.
\ea %那么，你倒说看看 ，你会有什么样的改变\ldots \jambox{(BCC)}
\gll \objex{na4me}, \objex{ni3} \objex{dao4} \obj{shuo1-kan4-kan4}, \objex{ni3} \objex{hui4} \objex{you3} \objex{shen2meyang4de} \objex{gai3bian4}\ldots\\
then you just say-look-look you will have what.kind.of change\\\jambox{(BCC)}
\glt `Then you just try and say what kind of changes you will have.'
\z

\ea %我得听看看你的条件再说\ldots \jambox{(BCC)}
\gll \objex{wo3} \objex{dei3} \obj{ting1-kan4-kan4} \objex{ni3de} \objex{tiao2jian4} \objex{zai4} \objex{shuo1}\ldots\\
I have.to listen-look-look your condition then say\\\jambox{(BCC)}
\glt `I'll have to listen to your conditions first before talking about it/ deciding.'
\z

A statistical comparison of the acceptability and the productivity of A-\obj{kan4-kan4} among speakers of different varieties of Mandarin Chinese has to be left for future studies.

\item
R2 comments on the following passage: The current study will only focus on the AA, A-yi-A, A-le-A, A-le-yi-A, ABAB and
AB-le-AB forms of verbal reduplication in Mandarin Chinese. AA-kan, A-kan-kan,
AAB, A-yi-AB, A-le-AB will also be mentioned.

### 2024-07-20 chapters/ch01-Intro.tex
Update 2024-07-20-20:23:56

\ea\label{ex:redup-ex} 
	\ea
	\gll qing ni chang zhe dao cai.\\
	please you taste this \textsc{clf} dish\\
	\glt `Please taste this dish.'

	\ex
	\gll qing ni \textit{chang}-\textit{chang} zhe dao cai.\\
	please you taste-taste this \textsc{clf} dish\\
	\glt `Please taste this dish a little bit.' 
	\z
\z

@@

The data in this paper was drawn from several sources.
In addition to introspection, the Modern Chinese subcorpus of the corpus of the \textit{Center for Chinese Linguistics of Peking University} ({CCL}) \citep{Zhanetal2003, Zhanetal2019} was also consulted. 
Further, examples from novels and plays written by native speakers were considered.

>>>>

\ea\label{ex:redup-ex} 
	\ea
	\gll \objex{qing3} \objex{ni3} \objex{chang2} \objex{zhe4} \objex{dao4} \objex{cai4}.\\
	please you taste this \textsc{clf} dish\\
	\glt `Please taste this dish.'

	\ex
	\gll \objex{qing3} \objex{ni3} \obj{chang2}-\objex{chang2} \objex{zhe4} \objex{dao4} \objex{cai4}.\\
	please you taste-taste this \textsc{clf} dish\\
	\glt `Please taste this dish a little bit.' 
	\z
\z

@@

The data in this paper was drawn from several sources.
In addition to introspection, the Modern Chinese subcorpus of the corpus of the \textit{Center for Chinese Linguistics of Peking University} ({CCL}) \citep{Zhanetal2003, Zhanetal2019} and the BCC corpus \citep{BCC} was also consulted. 
Further, examples from novels and plays written by native speakers were considered.
